Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-10-22 PaperMagneticProfiles_JBSMSE.tex
Begin developing literature review.

\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators
\thanks{
An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}).
}}

@@

A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and coold down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source. Different cycles can be devised by changing the duration and synchronization  between the two cycle \emph{characteristic waveforms}:

@@

In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied. Magnetic waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}. \colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}. Trevizoli et al.~\cite{bib:trevizoli16_perfor_model} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles. However, no systematic assessment of the effect of amplitude was performed nor did they investigate different geometries \colorbox{yellow}{nao estah claro o que vc quer dizer por geometries}.

>>>>

\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators
\thanks{
An abridged version of this manuscript was presented at the 24th ABCM International Congress of Mechanical Engineering (COBEM 2017), held in Curitiba, PR, Brazil, in December 2017.
}}

@@

A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and cooled down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, and decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source. Different cycles can be devised by changing the duration and synchronization  between the two cycle \emph{characteristic waveforms}:

@@

In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile. Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \citet{bib:bjoerk11_amr}. If this delay is further increased so that the fluid flow period can coincide with diferent stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle (with isothermal (de)magnetization steps) yield the highest values of the coefficient of performance \cite{bib:plaznik13-numer}. This conclusion was confirmed by the more extensive numerical analysis of \cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs which could generate these profiles.

\colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}. Trevizoli et al.~\cite{bib:trevizoli16_perfor_model} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles. However, no systematic assessment of the effect of amplitude was performed nor did they investigate different geometries \colorbox{yellow}{nao estah claro o que vc quer dizer por geometries}.
